---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# assignmentb2torinhalvorson

The goal of assignmentb2torinhalvorson is to calculate the standard deviation of a numeric vector, using the key function stdev(). 
This function takes a numeric parameter 'w' as input, removes missing values automatically, and returns the standard deviation. 
The mean and length of the vector are also printed. The function will automatically return an error if the input is not numeric. 
By using this package, the user can easily evaluate the standard deviation of any vector, including those with missing values, 
which has broad applications to statistical analysis.

## Installation

You can install the development version of assignmentb2torinhalvorson from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
# devtools::install_github("assignmentb2torinhalvorson", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to use the stdev function to calculate the standard deviation of a 

```{r example}
# library(assignmentb2torinhalvorson)
# vec <- c(1,10,20,24,25)
# stdev(vec)

```

